Figures

### 2015-12-16 figures.Rmd
Figure 1 legend (fixes #33)

\begin{figure*}
 \includegraphics{data/lmdFigure.pdf}
\end{figure*}
\captionof{figure}{Laser microdissection of meristem samples in the early stages of inflorescence development. Samples were collected from the rachis meristem (\textbf{a} and \textbf{e}), the primary branch meristem (\textbf{b} and \textbf{f}), the elongating primary branch meristem and axillary meristem (\textbf{c} and \textbf{g}) and the spikelet meristem (\textbf{d} and \textbf{h}). Images show the samples before (\textbf{a}–\textbf{d}) and after (\textbf{e}–\textbf{h}) dissection.}
\clearpage

>>>>

\begin{figure*}
 \includegraphics{data/lmdFigure.pdf}
\end{figure*}
\captionof{figure}{Laser microdissection of meristem samples in the early stages of inflorescence development. Samples were collected from the rachis meristem (\textbf{a} and \textbf{e}), the primary branch meristem (\textbf{b} and \textbf{f}), the elongating primary branch meristem and axillary meristem (\textbf{c} and \textbf{g}) and the spikelet meristem (\textbf{d} and \textbf{h}). Images show the samples before (\textbf{a}–\textbf{d}) and after (\textbf{e}–\textbf{h}) dissection. Scale bars represent \SI{200}{\micro\metre} (red, \textbf{a}--\textbf{c} and \textbf{e}--\textbf{g}) or \SI{320}{\micro\metre} (blue, \textbf{d} and \textbf{h}).}
\clearpage
